Imputation of incomplete multilevel data

### 2024-02-28 manuscript.qmd
Add Stef's recipes from FIMD

>>>>

> Recipe for a level-1 target: 
1.	Define the most general analytic model to be applied to imputed data; 
2.	Select a 2l method that imputes close to the data; 
3.	Include all level-1 variables; 
4.	Include the disaggregated cluster means of all level-1 variables; 
5.	Include all level-1 interactions implied by the analytic model; 
6.	Include all level-2 predictors; 
7.	Include all level-2 interactions implied by the analytic model; 
8.	Include all cross-level interactions implied by the analytic model; 
9.	Include predictors related to the missingness and the target; 
10.	Exclude any terms involving the target

> Recipe for a level-2 target: 
1.	Define the most general analytic model to be applied to imputed
data; 
2.	Select a 2lonly method that imputes close to the data; 
3.	Include the cluster means of all level-1 variables; 
4.	Include the cluster means of all level-1 interactions; 
5.	Include all level-2 predictors; 
6.	Include all interactions of level-2 variables; 
7.	Include predictors related to the missingness and the target; 
8.	Exclude any terms involving the target
